---
title: "About"
description: ""
date: 2022-07-14T17:17:55+02:00
lastmod: 2022-07-14T17:17:55+02:00
draft: false
images: []
toc: false
---

```{r setup, include=FALSE, echo=FALSE}
library(gtrendsR)
library(dplyr)
library(readr)
library(highcharter)
library(htmlwidgets)
library(here)

## Load proteinomics highcharts plot style settings
p_theme <- paste(here(), "proteinomics/highcharts/p_theme.rds", sep = "/") %>%
  read_rds()
p_chart_opts <- paste(here(), "proteinomics/highcharts/p_chart_opts.rds", sep = "/") %>%
  read_rds()
p_chart_opts()

```
```{r gtrends, echo=FALSE, error = TRUE, include=FALSE}
#get google trends data for web and news
#p_web <- gtrends(c("protein"), time="all")
#p_news <- gtrends(c("protein"), time="all", gprop=c("news"))

#pw <- as_tibble(p_web$interest_over_time)
#pn <- as_tibble(p_news$interest_over_time)

#pw$date <- as.Date(pw$date)
#pn$date <- as.Date(pn$date)

# sw_plot <- ggplot() +
#   geom_line(data = sw, aes(date,hits), color="red") +
#   geom_line(data = sn, aes(date,hits), color="blue")
# 
# sw_plot

# Get Google Trends data from csv
pw <- read_csv("gtrends.csv")
pw$Month <- as.Date(paste0(pw$Month, "-01"))

# Highchart version

p_chart <- highchart() %>%
 hc_add_series(pw, type="spline", name="Web search", hcaes(x = Month, y = protein)) %>%
# hc_add_series(pn, type="spline", name="News search", hcaes(x = date, y = hits)) %>%
  hc_xAxis(type = "datetime") %>%
  hc_yAxis(max=100) %>%
  hc_size(300, 300) %>%
  hc_title(text='"Protein" Search Popularity') %>%
  hc_subtitle(text="Google Trends") %>%
  hc_add_theme(p_theme())
```

proteinomics.org is the collection of data visualizations and resources describing the global protein economy. It is an entirely free, open-source tool created with the following aims:

1. Facilitate access to information about protein and related topics
2. Support more accurate and data-driven journalism, communications, and visual storytelling
3. Help elevate baseline levels of data and statistical numeracy
4. Foster engagement in open-source projects with potential for broad public benefit

proteinomics.org is not merely a resource for researching and reporting on protein-related topics, it is also a designed to make learning data visualization and analysis easier and more accessible for everyone.

### Why protein

<div class="about" style="display:block; width: 100%; flex-wrap: wrap;">
<div style="width: auto !important; float: right; margin-left: 10px;">
```{r gtrends_chart, echo=FALSE, error = TRUE}
p_chart
```
</div>
Protein is a topic of growing public interest. It is also a common theme of scientific and nutritional illiteracy. Online media and social media environments often contribute to confusion as sources of misinformation and culturally or ideologically biased reporting. proteinomics.org is a fact-checking tool that not only helps answer common questions, but also inspires users to look deeper and more critically at the issues.
</div>

### How to contribute

proteinomics.org is 100% open source and entirely built using free tools and software. Anyone with basic knowledge of R and git can contribute.

View the [readme on Github](https://github.com/proteinomics/proteinomics.org) to download the entire project or individual parts for local editing.

### Who

See the [credits page](/credits) for full details on data sources, software, tools, and project contributors.

proteinomics.org is currently being developed by [Protein Report](https://www.proteinreport.org).

### License

The content of this project itself is licensed under the [Creative Commons Attribution 3.0 Unported license](https://creativecommons.org/licenses/by/3.0), and the underlying source code used to format and display that content is licensed under the [MIT license](https://github.com/github/choosealicense.com/blob/gh-pages/LICENSE.md).
